\section{Scope of the System}

\subsection{In Scope}

LuxeWay is a Peer-to-Peer (P2P) rental marketplace that connects individual and business vehicle owners (Owners) with end-users (Consumers). The platform synthesizes two complementary service models: short-term \textbf{Car Sharing (CS)}, typically charged by the hour or day, and long-term \textbf{Car Rental (CR)}, enabling owners to maximize asset utilization across both market segments from a single listing interface.

The core functional capabilities delivered in this version include:

\begin{itemize}
    \item \textbf{Vehicle Listing Management:} Owners may list cars and motorbikes with full specifications (transmission, fuel type, seating capacity, add-on services), multi-image galleries, geo-tagged locations, and dynamic pricing rules.

    \item \textbf{Booking \& Reservation Workflow:} Consumers can search and filter vehicles by city, category, price range, transmission type, fuel type, and service attributes (chauffeur availability, airport delivery). Bookings support configurable rental periods, insurance tier selection, delivery options, and coupon redemption.

    \item \textbf{Identity Verification \& Access Control:} A four-tier role model (CUSTOMER, OWNER, ADMIN, SUPER\_ADMIN) is enforced through stateless JWT authentication, with KYC document upload and driving license verification workflows for Owners.

    \item \textbf{Secure Payment Processing:} All transactions are processed through \textbf{VNPay}, supporting Vietnamese bank cards, e-wallets (MoMo, ZaloPay), and international Visa/Mastercard. An in-app \textbf{LuxeWallet} digital balance enables instant settlement between parties.

    \item \textbf{Real-Time Communication:} A WebSocket-based messaging system (STOMP over SockJS) facilitates live chat between renters and owners, supplemented by a server-side push notification service for booking status updates.

    \item \textbf{Digital Contract Generation:} Upon booking confirmation, the platform automatically produces a legally structured PDF rental contract capturing all terms, vehicle condition, pricing breakdown, and party identities using the iText library.

    \item \textbf{Trust \& Reputation System:} A multi-dimensional review framework evaluates five independent dimensions --- vehicle cleanliness, information accuracy, owner communication, value for money, and delivery quality --- to produce composite trust scores for both vehicles and owners.

    \item \textbf{Dispute \& Support Management:} An integrated dispute resolution module and a Help Center knowledge base support post-rental conflict resolution and reduce reliance on manual customer service escalation.

    \item \textbf{Administration Dashboard:} Admin and Super Admin roles have access to full platform analytics, user management, vehicle approval workflows, coupon management, and system health monitoring.
\end{itemize}

\subsection{Out of Scope}

The following capabilities are explicitly excluded from the current version and are identified as directions for future work:

\begin{itemize}
    \item Native mobile applications (Android / iOS)
    \item AI-driven vehicle recommendation and dynamic pricing engine
    \item Blockchain and on-chain Smart Contract implementation
    \item Real-time GPS vehicle tracking
    \item Voice assistant and conversational UI support
    \item Cryptocurrency payment integration
\end{itemize}
