\section{Proposed Solution}

\subsection{Overview}

LuxeWay is implemented as a production-grade full-stack web application
organized into two independently deployable service boundaries: a
\textbf{React Single-Page Application (SPA)} serving the consumer and
owner interfaces, and a \textbf{Spring Boot RESTful API} encapsulating
all business logic, data persistence, and external service integration.

Although blockchain and Smart Contract capabilities identified in the
literature remain outside the current implementation scope, the
\textit{design principles} they embody---transactional atomicity, audit
immutability, automated condition enforcement, and privacy-preserving
identity management---are realized through analogous mechanisms within
the conventional stack: database transactions with optimistic locking,
append-only booking history tables, rule-based pricing automation, and
JWT-scoped data access.

\subsection{System Architecture}

\subsubsection{Frontend}

The client application is built on \textbf{React~18} with
\textbf{TypeScript}, bundled by \textbf{Vite~5}, and styled with
\textbf{Tailwind CSS~3} and \textbf{Radix UI} accessible component
primitives. State is managed globally via \textbf{Zustand} stores for
authentication, vehicle browsing, and wishlist. Additional libraries
include React Router~6.25 (routing), Framer Motion~11.3 (animation),
React Leaflet~4.2 (map display), i18next~26.2 (Vi/En i18n),
SockJS+STOMP (WebSocket messaging), React Hook Form + Zod~3.23 (form
validation), and Recharts~2.12 (dashboard visualization).

\subsubsection{Backend}

The server-side application is built on \textbf{Spring Boot~3.2.5}
running on \textbf{Java~21~LTS}, exposing a stateless RESTful API at
context path \texttt{/api/v1}. Table~\ref{tab:backend_stack} summarizes
the principal backend components.

\begin{table}[htbp]
\centering
\caption{Backend Technology Stack}
\label{tab:backend_stack}
\begin{tabular}{ll}
\toprule
\textbf{Technology} & \textbf{Purpose} \\
\midrule
Spring Boot 3.2.5 / Java 21  & REST API, embedded Tomcat \\
Spring Data JPA + Hibernate 6 & ORM, JPQL queries \\
Spring Security + JJWT 0.12.3 & JWT auth, RBAC, OAuth2 \\
Spring WebSocket + STOMP      & Real-time messaging \\
SpringDoc OpenAPI 2.5         & Swagger UI documentation \\
MapStruct 1.5                 & Entity-to-DTO mapping \\
iText 5.5                     & PDF contract generation \\
Apache Tika 2.9               & File upload MIME validation \\
Lombok 1.18                   & Boilerplate code generation \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Database}

\textbf{Microsoft SQL Server} serves as the primary relational data
store, managed through Hibernate schema validation (\texttt{ddl-auto:
none}) with explicit SQL schema scripts. The schema comprises over~40
tables organized into nine logical domains: Identity \& Access; Vehicle
Ecosystem (Cars); Vehicle Ecosystem (Motorbikes); Booking Lifecycle;
Payments; Trust \& Reviews; Communication; Support \& Knowledge; and
Platform Analytics. Schema initialization and seed data are applied
automatically on startup via Spring's \texttt{sql.init} subsystem.

\subsubsection{API Design}

The backend exposes a versioned RESTful API following standard HTTP
semantics. Principal endpoint groups include: \texttt{/auth/**}
(registration, login, token refresh, OAuth2); \texttt{/cars/**} and
\texttt{/motorbikes/**} (listing, search, booking); \texttt{/payments/**}
(VNPay checkout and callback); \texttt{/reviews/**} (post-rental
submission); \texttt{/users/**} (profile, KYC upload); and
\texttt{/admin/**} (ADMIN/SUPER\_ADMIN only). CORS is configured
globally to permit \texttt{localhost:5173} and production frontend
origins with \texttt{AllowCredentials: true}.

\subsection{Strategic Business Model}

LuxeWay operationalizes the hybrid CR+CS model validated by Soppert
et al.~\cite{soppert2024benefit} by maintaining two structurally
independent vehicle ecosystems---\textbf{Cars} and
\textbf{Motorbikes}---under a unified owner dashboard. This architecture
is hypothesized to increase per-owner revenue in the 23--120\% range
documented for commercial fleet operators~\cite{soppert2024benefit},
adapted to the P2P context where individuals constitute the supply side.

A transparent fee structure applies at checkout: a 12\% service fee
and 8\% tax on the base rental price, consistent with Vietnamese
e-commerce norms. Insurance tiers (basic, premium, zero-deductible),
delivery fees, add-on packages (chauffeur, airport delivery, wedding),
and coupon codes are composited into the final booking total prior to
VNPay initiation.

\subsection{Security Architecture}

\subsubsection{Authentication and Session Management}

LuxeWay implements stateless JWT authentication (RFC~7519). Login
issues a signed access token (24\,h expiry) and refresh token (7\,d
expiry) via HS256. The frontend client intercepts 401 responses,
silently refreshes the token, and retries the original request.
OAuth2 via Google is supported; the backend links the OAuth2 identity
to an existing account by email or creates a new one, then issues an
equivalent JWT pair.

\subsubsection{Role-Based Access Control}

Authorization is enforced at two layers. \texttt{HttpSecurity}
\texttt{requestMatchers} rules restrict paths by HTTP method and
role---e.g., \texttt{GET /cars/**} is public while \texttt{POST /cars}
requires \texttt{OWNER} or \texttt{ADMIN}. Service-layer
\texttt{@PreAuthorize} annotations enforce ownership constraints at
the business logic level.

\subsubsection{Payment and File Security}

A custom \texttt{VNPayIPWhitelistFilter} validates that VNPay callbacks
originate exclusively from declared VNPay server IPs, preventing spoofed
callback injection. Uploaded files are validated by Apache Tika's
MIME-type detector against declared \texttt{Content-Type}, mitigating
polyglot file upload attacks.

\subsection{Multi-Dimensional Review System}

Following the framework of Neifer et al.~\cite{neifer2024trust},
LuxeWay replaces a single-axis star rating with a five-dimension model
applied per verified completed booking (Table~\ref{tab:review_dims}).
Each dimension is scored 1--5; the composite rating is the arithmetic
mean. Mandatory booking linkage eliminates unverified submissions,
reducing the manipulation risk documented in~\cite{hu2019sharing}.

\begin{table}[htbp]
\centering
\caption{Five-Dimension Review Model}
\label{tab:review_dims}
\begin{tabular}{ll}
\toprule
\textbf{Dimension} & \textbf{Evaluated Aspect} \\
\midrule
Vehicle Cleanliness  & Physical condition at pickup \\
Listing Accuracy     & Description vs.\ actual vehicle \\
Owner Communication  & Responsiveness and professionalism \\
Value for Money      & Quality-to-price ratio \\
Delivery Quality     & Timeliness of vehicle delivery \\
\bottomrule
\end{tabular}
\end{table}
