\section{Conclusion}

This paper has presented the design rationale, architectural decisions, and implementation approach of \textbf{LuxeWay} --- a peer-to-peer vehicle rental marketplace developed for the Vietnamese market. Through a systematic analysis of incumbent platforms and a structured review of the academic literature, the work identified four persistent gaps in existing systems: the absence of production-grade P2P implementations, insufficient support for hybrid CR+CS business models in the P2P context, neglect of UX-centered system documentation, and the limitations of subjective-only reputation systems.

LuxeWay addresses each of these gaps through deliberate engineering choices. The full-stack architecture --- \textbf{React 18 + TypeScript} on the frontend and \textbf{Spring Boot 3 / Java 21} on the backend, backed by \textbf{Microsoft SQL Server} --- delivers a deployable, maintainable system that embodies the behavioral principles of secure, transparent P2P rental without incurring the operational complexity of blockchain deployment. The hybrid Car and Motorbike listing ecosystem validates Soppert et al.'s \cite{soppert2024benefit} revenue optimization thesis in a P2P context. The multi-dimensional review protocol adapts Neifer et al.'s \cite{neifer2024trust} objectivity argument to a hardware-free implementation accessible to individual owners. The VNPay + LuxeWallet payment infrastructure localizes the trust-and-escrow principles of Smart Contract payment systems \cite{madhusudan2019applying} to the Vietnamese regulatory and banking environment.

Findings from related studies confirm that platforms combining Car Rental and Car Sharing models can achieve significant economic benefits for both vehicle owners and consumers \cite{elhog2025decentralized, soppert2024benefit}. By grounding implementation decisions in the academic literature while remaining pragmatic about deployment constraints, LuxeWay demonstrates that a trustworthy, feature-complete P2P rental marketplace is achievable with conventional web technologies when architectural principles are applied with rigor.

Future work will explore the integration of AI-driven vehicle recommendation, native mobile application development, and --- as the Vietnamese regulatory landscape matures --- selective incorporation of smart contract escrow mechanisms for high-value rental transactions.
